\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Consultant-II}
    {Deloitte \& Touche AERS India Pvt. Ltd.}
    {Sep 2014 - Present}
    {Hyderabad, India}
    {
      \begin{cvitems}
      	\item {Performed full-scale validation of forecasting models for Pre-Provisions Net Revenue (PPNR) and Balance Sheet (BSM) Origination Volumes for a leading US Bank. The scope of work included assessing the theoretical soundness, economic rationale, statistical testing and related inferences across the models.}
        \item {Conducted assessment of the Bank's Model Development and Validation Framework for alignment with best industry practices and Supervisory Guidance on Model Risk Management (CCAR and SR 11/7).}
        \item {Conducted independent Annual Model Reviews for Credit Scorecard Models, assessing the model inputs and outputs, as an ongoing risk governance exercise for a leading US Bank.}
        \item {Developed \LaTeX\  classes and packages for the documentation of modeling methodologies and review processes per the latest guidelines for the Quality Check and Review team of the Bank.}
        \item {Performed valuations of fixed income instruments; derivatives on interest rates, foreign exchange, equity and credit; structured products like mortgage backed securities and loan instruments for Securities Pricing Center at Deloitte.}
        \item {Analyzed a portfolio allocation model, for an advisory engagement, and devised mitigation methodology for the observed errors in the estimation.}
        \item {Determined Value at Risk (VaR) for clients based on their portfolio positions and historic market movements as a part of Audit Support.}
        \item {Developed Python based tools to conduct testing for multiple Hedge Effectiveness testing projects.}
      \end{cvitems} }

\end{cventries}
